---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# String Operations - sto

<!-- badges: start -->
<!-- badges: end -->

The goal of {sto} is to make some operations with strings and text analysis easier.
One of the functions make it easier to create vectors from string and other operations with `grep`, `grepl` and `gsub` in native pipe.
sto also have functions to fine grain generate stopwords lists by language and grammar categories.
Also comes with a rule based proper name/entity extractor in the form of list or graph.

Keywords: strings; text analysis; text mining

## Installing String Operations

Install using {devtools} package

```{r eval=FALSE}
install.packages("devtools") # if devtools is not installed yet
devtools::install_github("SoaresAlisson/sto")
```

Or install using {pak} package
```{r, eval=FALSE}
install.packages("pak", dependencies = TRUE) # if {pak} is not installed yet
pak::pkg_install("SoaresAlisson/sto")
```

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

See the vignettes.
