---
title: "Generating stopwords"
subtitle: "Generate a list of stopwords using grammar categories"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{stopwords}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This functions is still under development
At this time you can generate a stopwords list
in Portuguese and English.

There is many options of stopwords lists available in R, like: 
- 
But none is categorized allowing a more fine grained control of the words by grammar categories.

```{r setup}
library(sto)
```

Choose the language and which grammar tags use to generate a stopword list.
The 
`lang` parameter uses the two word designation, and the 
`cat` designs the grammar category following Penn Treebank. See [here](https://www.ling.upenn.edu/courses/Fall_2003/ling001/penn_treebank_pos.html)

| POS Tag |	Description |	Example | Description |
|-----|-----|-----|----|
| CC  |coordinating conjunction|and||
| CD  |cardinal number |	one, third ||
| DT  |determiner |	the ||
| EX  |existential | there 	there is ||
| PP  | pronoum | me, you, he, she, it, we, they ||
| PPZ | pronoum|||
| UH  | interjection | oops! ||
|  V  | verb | are be have |variations of verbs to be, have, |

```{r gen_stopwords}
gen_stopwords()
gen_stopwords(lang = "en", categories = "CC")
gen_stopwords(lang = "pt", categories = "CC DT")
# to convert the list into a named vector
gen_stopwords(lang = "en", categories = "CC DT V") |> unlist()

gen_stopwords(lang = "pt")
gen_stopwords(lang = "pt", categories = "V")
```

With the `vec` parameter, it is possible to have three different output formats: 
list (default), vector and named vector.

```{r genSW list vec}
gen_stopwords(lang = "pt", categories = "V", vec = "list")
gen_stopwords(lang = "pt", categories = "V", vec = "vec")
gen_stopwords(lang = "pt", categories = "V", vec = "n_vec")
```



To use only certain kinds of verbs, like only the variations/conjugations of the Portuguese verb `ser`:
```{r verb$ser}
my_sw <- gen_stopwords("pt", "V", vec = "list")
my_sw$V$ser
# or shorter
gen_stopwords("pt", "V", vec = "list")$V$seb
```



